Verifying Demonstrations

### 2018-02-26 paper/SystemModel.tex
system model edits and some questions in comments regarding the identifiers in the definitions. only a label added in the protocol for referencing.

The organizer Alice want to count everyone who participated at any time and in 
any of the locations~\cite{2016DemonstrationsInSeoul}.
(Whereas police are only interested in the maximum crowd at any point in time, 
to deploy enough personnel for crowd-control.)
We will define a protest as an event that is uniquely identified by its cause 
(\(id\) below), its time interval (\(t\)) and its location (area \(l\)).
More specifically, we will use the following definition.

\begin{definition}[Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((cid, t, l)\) where
  \(cid\in \Z_{2^\lambda}\) is the cause\footnote{%
    I.e.\ the cause of the protest.
  } identifier,
  \(t = \interval{t_s}{t_e}\subseteq \R\) is a time interval and
  \(l = N_\epsilon(x, y)\subseteq \R^2\) is the location (an 
  \(\epsilon\)-neighbourhood of \((x,y)\)).
  A \emph{protest} is a set of subprotests sharing the same \(id\).
\end{definition}

@@

\subsection{Participation and count}

Each participant who want to be counted must submit a participation proof.
The proof must be associated with the protest, i.e.\ its identifier \(cid\), 
time and location must coincide with any of its subprotests.
We use witnesses to associate the proof to the location by creating a proof 
share.
% XXX what is a witness?
A witness is only allowed to create one proof share per protester.
The proof and its proof shares are stored in a set, as there should be only 
unique proof shares.

\begin{definition}[Participation-proof share]
  A \emph{participation-proof share} \(w = (pid, cid, t, l, wid)\) is a tuple 
  where
  \(cid, t, l\) are as in \cref{DefProtest},
  \(pid\) is unique for a protester--\(cid\) pair, and
  \(wid\) is unique for a witness--protester pair.
  We let \(W\) be the set of all proof shares.
\end{definition}

>>>>

The organizer Alice wants to count everyone who participated at any time and in 
any of the locations~\cite{2016DemonstrationsInSeoul}.
(Whereas police are only interested in the maximum crowd at any point in time, 
to deploy enough personnel for crowd-control.)
We will define a protest as an event that is uniquely identified by its cause 
(\(id\) below), its time interval (\(t\)) and its location (area \(l\)).
More specifically, we will use the following definition.

\begin{definition}[Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((cid, t, l)\) where
  \(cid\in \Z_{2^\lambda}\) is the identifier of the cause of the protest,
  \(t = \interval{t_s}{t_e}\subseteq \R\) is a time interval and
  \(l = N_\epsilon(x, y)\subseteq \R^2\) is the location (an 
  \(\epsilon\)-neighbourhood of \((x,y)\)).
  A \emph{protest} is a set of subprotests sharing the same \(id\).
\end{definition}

@@

\subsection{What is a proper count?}

Each participant who wants to be counted must submit a participation proof.
The proof must be associated with the protest, i.e.\ its identifier \(cid\), 
time and location must coincide with any of its subprotests.

In practical terms, participants witness each other's particpation
using their smartphones running the protocol described in
Section~\ref{protocol} and uploading their testimony to a blockchain
after the protest.

More formally, we use witnesses to associate the proof to the location by creating a proof 
share.
% XXX what is a witness?
A witness is only allowed to create one proof share per protester.
The proof and its proof shares are stored in a set, as there should be only 
unique proof shares.

\begin{definition}[Participation-proof share]
  A \emph{participation-proof share} \(w = (pid, cid, t, l, wid)\) is a tuple 
  where
  \(cid, t, l\) are as in \cref{DefProtest},
  \(pid\) is unique for a protester--\(cid\) pair, and
  \(wid\) is unique for a witness--protester pair.
  We let \(W\) be the set of all proof shares.
\end{definition}
%Sonja asks: do the same pair of people (witness-protester) get the
%same wid on a different protest? The pid is unique for protester-cid
%pair thus the id of a protester at a particular protest. Pid is thus
%derived from the protester id (which has no term) and the protest id
%(cid)? In analogy, wid is derived from pid (and thus cid) of both
%participants, protesters i and j, say, where i witnesses j at cid and
%simultaneously symmetrically j witnesses i?
%Using wid and w is confusing since we changed the terminology to use
%proof shares instead of the previous witness (as in testimony, not
%person). wid sounds like it would be the id of the witness person,
%pid sounds like it would be the id of the protester being witnessed,
%we have defined neither and they might not be needed, but it is
%confusing to read.
